Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2018-10-24 awipev-CO2.Rmd
changement des paths pour les readtable/loads/ggsave/save

```{r Read and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
# xx <- read_tsv("../fb_server/ny-alesund/data/old/All_sensors_731101_2016-08-20.txt", skip=16, col_names=TRUE)
load(file = "../fb_server/shinyroot/AWIPEV-CO2/nydata_hour_shiny.Rdata")
#load(file = "../fb_server/shinyroot/AWIPEV-CO2/nydata_shiny.Rdata") #d
# load = d_hour
d_hour <- d_hour %>%
  dplyr::select(-date) %>%
  dplyr::mutate(AT = ifelse(datetime > "2016-02-26 12:00:00", AT, NA), # beginning of data series for AT
         AT = ifelse(AT == "NaN", NA, AT), #3 columns are character
         pH_AT = ifelse(pH_AT == "NaN", NA, pH_AT),
         PCO2_Corr_Zero2 = ifelse(PCO2_Corr_Zero2 %in% c("NaN", 66666), NA, PCO2_Corr_Zero2)
         ) %>%
  dplyr::rename(at_contros=AT, ph_at_contros=pH_AT, pco2_contros=PCO2_corr_contros_filtered, zero_contros=PCO2_Corr_Zero2, 
         sal_fb=Salinity_filtered, temp_fb=Temperature_filtered, pH_durafet=HW_pH1_filtered, temp_insitu=Temp_SBE38_filtered)
```

@@

save(file="../fb_data/d_all.Rdata", d_all)

@@

ggsave("../fb_figures/TA_Analyser/Calibration/TA_calibration_CRM.png", calib_p, units="cm")
print(calib_p)
```

@@

```{r First period plot, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"}
# Plot of regression
p <- ggplot(calib_ta_first%>%filter(diff_ta <= 50),aes(datetime,diff_ta)) + 
    geom_point() + geom_smooth(method='lm', se=FALSE)+ 
    geom_point(data= calib_ta_first%>%filter(diff_ta >= 50), aes(x=datetime, y=diff_ta), color="red")  +
  geom_hline(yintercept = 0, linetype="dashed" )+
  labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                     "Intercept =",signif(fit$coef[[1]],5 ),
                     "Slope =",signif(fit$coef[[2]], 5),
                     "P =",signif(summary(fit)$coef[2,4], 5))) + 
  ylab("Difference: Reference - Analyser") + xlab("Time") + scale_x_datetime(date_labels = "%b %Y", date_minor_breaks = "month", timezone="UTC")
print(p)
ggsave("../fb_figures/TA_Analyser/Calibration/Diff_ref_TA_first_period.png", p, units="cm")
```

@@

```{r Third period plot, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"}
# Plot of regression
p <- ggplot(calib_ta_third,aes(x=datetime, y=diff_ta) )+ 
    geom_point() + geom_smooth(method='lm', se=FALSE)+ 
    #geom_point(data= calib_ta_third%>%filter(diff_ta < -40 & diff_ta<20), aes(x=datetime, y=diff_ta), color="red")  +
   geom_hline(yintercept = 0, linetype="dashed" )+
  geom_vline(xintercept = as.POSIXct("2018-01-08 12:55:00", tz="UTC"), colour="red", linetype = "longdash") +
  #geom_text(aes(xintercept=as.POSIXct("2018-01-01 12:55:00"),label="TA "), colour="red", vjust=1.2)+
  labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                     "Intercept =",signif(fit$coef[[1]],5 ),
                     " Slope =",signif(fit$coef[[2]], 5),
                     " P =",signif(summary(fit)$coef[2,4], 5))) + ylab("Difference: Reference - Analyser") + xlab("Time") + 
  scale_x_datetime( date_labels = "%b %Y", date_minor_breaks = "month", timezone="UTC")
print(p)
ggsave("../fb_figures/TA_Analyser/Calibration/Diff_ref_TA_third_period.png", p, units="cm")
```

@@

ggsave("../fb_figures/Discrete_TA_salinity_AWIPEV.png", at_s, width=15, height =10, units="cm")

@@

```
The relationship between the Contros and calculated *p*CO~2~ is not good at all in the sense that it is far from the 1:1 line, despite a good r2 (`r round(fit$rsquare, digits=2)`).
```{r plot measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
print(pco2calc_pCO2_contros_text)
ggsave("../fb_figures/pco2calc_pCO2_contros.png", pco2calc_pCO2_contros_text, width=5, height=5, units="cm")
```

@@

pdelta_at_snapo
pdelta_at_snapo_dygraph
pdelta_ct_snapo
pdelta_ct_snapo_dygraph
ggsave("../fb_figures/SNAPO/delta_at_awipev_snapo.png", pdelta_at_snapo, units="cm")
ggsave("../fb_figures/SNAPO/delta_ct_awipev_snapo.png", pdelta_ct_snapo, units="cm")
```

>>>>

```{r Read and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
# xx <- read_tsv("../fb_server/ny-alesund/data/old/All_sensors_731101_2016-08-20.txt", skip=16, col_names=TRUE)
load(file = paste0(path, "fb_server/shinyroot/AWIPEV-CO2/nydata_hour_shiny.Rdata"))
#load(file = "../fb_server/shinyroot/AWIPEV-CO2/nydata_shiny.Rdata") #d
# load = d_hour
d_hour <- d_hour %>%
  dplyr::select(-date) %>%
  dplyr::mutate(AT = ifelse(datetime > "2016-02-26 12:00:00", AT, NA), # beginning of data series for AT
         AT = ifelse(AT == "NaN", NA, AT), #3 columns are character
         pH_AT = ifelse(pH_AT == "NaN", NA, pH_AT),
         PCO2_Corr_Zero2 = ifelse(PCO2_Corr_Zero2 %in% c("NaN", 66666), NA, PCO2_Corr_Zero2)
         ) %>%
  dplyr::rename(at_contros=AT, ph_at_contros=pH_AT, pco2_contros=PCO2_corr_contros_filtered, zero_contros=PCO2_Corr_Zero2, 
         sal_fb=Salinity_filtered, temp_fb=Temperature_filtered, pH_durafet=HW_pH1_filtered, temp_insitu=Temp_SBE38_filtered)
```

@@

save(file= paste0(path, "fb_data/d_all.Rdata"), d_all)

@@

ggsave(paste0(path, "fb_figures/TA_Analyser/Calibration/TA_calibration_CRM.png"), calib_p, units="cm")
print(calib_p)
```

@@

```{r First period plot, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"}
# Plot of regression
p <- ggplot(calib_ta_first%>%filter(diff_ta <= 50),aes(datetime,diff_ta)) + 
    geom_point() + geom_smooth(method='lm', se=FALSE)+ 
    geom_point(data= calib_ta_first%>%filter(diff_ta >= 50), aes(x=datetime, y=diff_ta), color="red")  +
  geom_hline(yintercept = 0, linetype="dashed" )+
  labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                     "Intercept =",signif(fit$coef[[1]],5 ),
                     "Slope =",signif(fit$coef[[2]], 5),
                     "P =",signif(summary(fit)$coef[2,4], 5))) + 
  ylab("Difference: Reference - Analyser") + xlab("Time") + scale_x_datetime(date_labels = "%b %Y", date_minor_breaks = "month", timezone="UTC")
print(p)
ggsave(paste0(path, "fb_figures/TA_Analyser/Calibration/Diff_ref_TA_first_period.png"), p, units="cm")
```

@@

```{r Third period plot, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"}
# Plot of regression
p <- ggplot(calib_ta_third,aes(x=datetime, y=diff_ta) )+ 
    geom_point() + geom_smooth(method='lm', se=FALSE)+ 
    #geom_point(data= calib_ta_third%>%filter(diff_ta < -40 & diff_ta<20), aes(x=datetime, y=diff_ta), color="red")  +
   geom_hline(yintercept = 0, linetype="dashed" )+
  geom_vline(xintercept = as.POSIXct("2018-01-08 12:55:00", tz="UTC"), colour="red", linetype = "longdash") +
  #geom_text(aes(xintercept=as.POSIXct("2018-01-01 12:55:00"),label="TA "), colour="red", vjust=1.2)+
  labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                     "Intercept =",signif(fit$coef[[1]],5 ),
                     " Slope =",signif(fit$coef[[2]], 5),
                     " P =",signif(summary(fit)$coef[2,4], 5))) + ylab("Difference: Reference - Analyser") + xlab("Time") + 
  scale_x_datetime( date_labels = "%b %Y", date_minor_breaks = "month", timezone="UTC")
print(p)
ggsave(paste0(path, "fb_figures/TA_Analyser/Calibration/Diff_ref_TA_third_period.png"), p, units="cm")
```

@@

ggsave(paste0(path, "fb_figures/Discrete_TA_salinity_AWIPEV.png"), at_s, width=15, height =10, units="cm")

@@

```
The relationship between the Contros and calculated *p*CO~2~ is not good at all in the sense that it is far from the 1:1 line, despite a good r2 (`r round(fit$rsquare, digits=2)`).
```{r plot measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
print(pco2calc_pCO2_contros_text)
ggsave(paste0(path, "fb_figures/pco2calc_pCO2_contros.png"), pco2calc_pCO2_contros_text, width=5, height=5, units="cm")
```

@@

pdelta_at_snapo
pdelta_at_snapo_dygraph
pdelta_ct_snapo
pdelta_ct_snapo_dygraph
ggsave(paste0(path, "fb_figures/SNAPO/delta_at_awipev_snapo.png"), pdelta_at_snapo, units="cm")
ggsave(paste0(path, "fb_figures/SNAPO/delta_ct_awipev_snapo.png"), pdelta_ct_snapo, units="cm")
```
